The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-21 analysis/paper/paper.qmd
Add function to get top words per topic

# Add latitude and longitude information to theses data frame
emu_theses <- geocode_thesis_locations(emu_theses, location = NULL)

@@

# The top 10 words that are the most common in each topic
emu_theses_top_terms <- emu_theses_topics |> 
  group_by(topic) |> 
  top_n(20, beta) |> 
  ungroup() |> 
  arrange(topic, -beta)

>>>>

# Add latitude and longitude information to theses data frame
emu_theses <- geocode_thesis_locations(emu_theses)

@@

# The top 10 words that are the most common in each topic
emu_theses_top_terms <- get_top_words_per_topic(emu_theses_topics, 20, "topic", "beta")
